fdcoexist

### 2018-08-31 paper_simulations.Rmd
Remove K, set B to be larger than A

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
K         <- 150  # Carrying capacity
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar
B = 0.005 # Scalar for intraspecific competition
d = 0.08 # Dispersal percentage

@@

The equation above only considers inter-specific competition when $j \neq i$ in the sum. We can however add intra-specific competition when $j = i$. Each site has a species-specific carrying capacity $K$ as the number of individuals approaches this carrying capacity the intra-specific competition increases:
\begin{equation}
\alpha_{ii} = \frac{K}{K - N_{t,i,x}}
\end{equation}

@@

\begin{equation}
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
B \times \frac{K}{K - N_{t, i, x}}
}
\end{equation}

with $A$ the coefficient scaling inter-specific competition and $B$ the one for intra-specific competition. Depending on the scenario we can suppose that $B < A$

@@

```{r simul_no_compet_no_corr}
no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_no_compet_low_cor}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_no_compet_high_cor}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_compet_no_corr}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_compet_low_corr}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

```{r simul_compet_high_corr}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = env_width,
                 K = K)
    })

@@

no_compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_compet_no_corr var_strength}
compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width,
                 K = K)
    })

@@

```{r simul_compet_low_corr var_strength}
compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width, K = K)
    })

@@

```{r simul_compet_high_corr var_strength}
compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = var_width, K = K)
    })

>>>>

n_patches <- 25   # Number of patches
n_species <- 100  # Number of species
n_gen     <- 150  # Length of model run (generations)
initpop   <- 50   # initial population size
n_traits  <- 3    # number of traits
k         <- 1.15 # Maximum growth rate
env_width <- seq(10, 10, length.out = n_patches)  # Envtal filter strength
var_width <- seq(10, 1, length.out = n_patches) # Varying envtal filter strength

# Competition + Dispersion coefficients
B = 1/500 # Scalar for intraspecific competition
A =  B/n_species	# Alpha scalar
d = 0.05 # Dispersal percentage

@@

The equation above only considers inter-specific competition when $j \neq i$ in the sum. We can however add intra-specific competition when $j = i$. Each site has a species-specific carrying capacity $K$ as the number of individuals approaches this carrying capacity the intra-specific competition increases:
\begin{equation}
\alpha_{ii} = B \times \N_{t,i,x}
\end{equation}

@@

\begin{equation}
N_{t+1, i, x} = \frac{
k \times \exp\left(- \displaystyle\frac{(\text{trait}_i - \text{env}_x)^2}{2\times \text{width}^2}\right) \times N_{t, i, x}}{
1 + A \times \displaystyle\sum_{j = 1,~j \neq i}^{S} N_{t, j, x}  (1 - \delta_{ij}) +
B \times \N_{t,i,x}
}
\end{equation}

with $A$ the coefficient scaling inter-specific competition and $B$ the one for intra-specific competition.

@@

```{r simul_no_compet_no_corr}
no_compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_no_compet_low_cor}
no_compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_no_compet_high_cor}
no_compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_compet_no_corr}
compet_no_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_compet_low_corr}
compet_low_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = env_width)
    })

@@

```{r simul_compet_high_corr}
compet_high_cor <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = env_width)
    })

@@

no_compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_no_compet_low_cor var_strength}
no_compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = low_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_no_compet_high_cor var_strength}
no_compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = high_cor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = 0, B = B, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_compet_no_corr var_strength}
compet_no_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B=B, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_compet_low_corr var_strength}
compet_low_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B=B, d = d,
                 k = k, width = var_width)
    })

@@

```{r simul_compet_high_corr var_strength}
compet_high_cor_var <- lapply(
    trait_scenarios,
    function(x){
        multigen(traits = uncor_traits,
                 trait_weights = x,
                 env = env,
                 time = n_gen,
                 species = n_species,
                 patches = n_patches,
                 composition = composition,
                 A = A, B = B, d = d,
                 k = k, width = var_width)
    })
